New_Data_Coherence

### 2019-08-25 Analysis/Coherence_Calculations_New.Rmd
point to new coherence path

```{r}
#Repeating for string

data_dir = "./data/"

#Read in new string database

string = read_table2(paste0(data_dir,"9606.protein.links.v11.0.txt.gz"))

string = string %>% mutate(protein1 = gsub("9606.", "", protein1), 
                             protein2 = gsub("9606.", "", protein2))

#Read in ensemble protein ID

ensembl = biomaRt::useEnsembl(biomart="ensembl", dataset="hsapiens_gene_ensembl", mirror = "www")

#Get gene set
genes = biomaRt::getBM(attributes=c('ensembl_peptide_id','hgnc_symbol'), mart = ensembl)

#Join gene names with string

string = left_join(string, genes, by = c("protein1" = "ensembl_peptide_id", "protein2" = "ensembl_peptide_id"))

#Rename to work with our functions

string = string %>% dplyr::rename(hgnc_symbol_a = hgnc_symbol)

#Repeat for second set of proteins

string = left_join(string, genes, by = c("protein2" = "ensembl_peptide_id"))

string = string %>% dplyr::rename(hgnc_symbol_b = hgnc_symbol)

string_filt = string %>% filter(combined_score>=500)

dim(string)
```

```{r}
#Reading in biogrid data

links = read_tsv("./data/BIOGRID-ALL-3.5.174.mitab.txt")

#Select human protein-protein interactions

links = links %>% filter(`Taxid Interactor A` == "taxid:9606" & `Taxid Interactor B` == "taxid:9606")

#Split based on Biogrid ID system then pull out gene names

protein1 = lapply(strsplit(links$`Alt IDs Interactor A`, "locuslink:"), function(x) strsplit(x[2], "\\|")[[1]][1])
protein2 = lapply(strsplit(links$`Alt IDs Interactor B`, "locuslink:"), function(x) strsplit(x[2], "\\|")[[1]][1])

protein1 = unlist(protein1)
protein2 = unlist(protein2)

#Place into matrix in form that disease2frame works on

links = links %>% mutate(protein1 =protein1, 
                             protein2 = protein2) %>% dplyr::select(protein1, protein2)

links = links %>% dplyr::select(hgnc_symbol_a = protein1,hgnc_symbol_b = protein2)

dim(links)
```

```{r}
#Read in edges generated from Connectivity_Comparison_*.Rmd

disease_overall_string = readRDS("string_edges_new.rds")

disease_overall_string_filt = readRDS("string_filt_edges_new.rds")

disease_overall_biogrid = readRDS("biogrid_edges_new.rds")

#Calculate slopes for all diseases under each category

dis_slopes_string_count = disease_overall_string %>% filter(Internal != 0) %>% filter(Category != "Random") %>% filter(Category != "KEGG") %>% 
    group_by(Disease, Category) %>% mutate(Count = n()) %>% group_by(Disease, Category, Count) %>%
    do({
      mod = lm(sqrt(External) ~ sqrt(Internal)-1, data = .)
      data.frame(Slope= coef(mod)[1])
    }) %>% arrange(Slope) %>% filter(Count>4)

dis_slopes_string_filt_count = disease_overall_string_filt %>% filter(Internal != 0) %>% filter(Category != "Random") %>% filter(Category != "KEGG") %>% 
    group_by(Disease, Category) %>% mutate(Count = n()) %>% group_by(Disease, Category, Count) %>%
    do({
      mod = lm(sqrt(External) ~ sqrt(Internal)-1, data = .)
      data.frame(Slope= coef(mod)[1])
    }) %>% arrange(Slope) %>% filter(Count>4)

dis_slopes_biogrid_count = disease_overall_biogrid %>% filter(Internal != 0) %>% filter(Category != "Random") %>% filter(Category != "KEGG") %>% 
    group_by(Disease, Category) %>% mutate(Count = n()) %>% group_by(Disease, Category, Count) %>%
    do({
      mod = lm(sqrt(External) ~ sqrt(Internal)-1, data = .)
      data.frame(Slope= coef(mod)[1])
    }) %>% arrange(Slope) %>% filter(Count>4)

#Running coherence for string

#Read in KEGG pathways for coherence
msig = readRDS("KEGG_String.rds")
msig =msig %>% filter(Category == "CP:KEGG")
coherence_tab = bind_rows()
for (i in unique(dis_slopes_string_count$Disease)) {
  #Filter to only include specific disease coherence
  dis = dis_slopes_string_count %>% ungroup() %>% filter(Disease == i)
  #Get closest KEGG pathways in term of gene counts
  msigs = msig %>% mutate(Num_Genes = abs(Count-dis$Count)) %>% arrange(Num_Genes)
  #Take top 10 KEGG pathways
  msigs = msigs[msigs$Num_Genes %in% unique(msigs$Num_Genes)[1:10],]

  diseases = bind_rows()
  #Generate random networks
  j = 1
    while(j<11) {
    #Sample gene networks equal in size to disease count
    diseases_curr = GeneSample(dis$Count, string, directed = FALSE)
    #Get random gene networks
    diseases_curr = data.frame(Gene = names(diseases_curr$internal_connectivity), Internal = sqrt(diseases_curr$internal_connectivity), External = sqrt(diseases_curr$external_connectivity))

    #Repeat if there are no internal edges
    if (any(diseases_curr$Internal !=0)) {
      j = j+1
      diseases = bind_rows(diseases, diseases_curr)

    }
    }
    #Calculate overall slope of random disease networks
      mod_rand = lm(External ~ Internal-1, data = diseases)
      rand_slope = coef(mod_rand)[[1]]

      #Normalize based on random slope and the median of kegg slopes (More robust)
      coherence = (dis$Slope - rand_slope)/(median(msigs$Slope, na.rm = TRUE)-rand_slope)
      coherence = data.frame(Disease = dis$Disease, Coherence = coherence, Msig_Norm = median(msigs$Slope, na.rm = TRUE), Rand_Norm = rand_slope )      
      coherence_tab = bind_rows(coherence, coherence_tab)
      saveRDS(coherence_tab, "coherence_string.rds")
}

```{r}
msig = readRDS("KEGG_String_Filt.rds")
msig =msig %>% filter(Category == "CP:KEGG")
coherence_tab = bind_rows()
for (i in unique(dis_slopes_string_filt_count$Disease)) {
  print(i)
  dis = dis_slopes_string_filt_count %>% filter(Disease == i)
  msigs = msig %>% mutate(Num_Genes = abs(Count-dis$Count)) %>% arrange(Num_Genes)
  msigs = msigs[msigs$Num_Genes %in% unique(msigs$Num_Genes)[1:10],]

  diseases = bind_rows()
  j = 1
    while(j<11) {
    diseases_curr = GeneSample(dis$Count, string, directed = FALSE)
    diseases_curr = data.frame(Gene = names(diseases_curr$internal_connectivity), Internal = sqrt(diseases_curr$internal_connectivity), External = sqrt(diseases_curr$external_connectivity))
    if (any(diseases_curr$Internal !=0)) {
      j = j+1
      diseases = bind_rows(diseases, diseases_curr)

    }
    }

      mod_rand = lm(External ~ Internal-1, data = diseases)
      rand_slope = coef(mod_rand)[[1]]

      coherence = (dis$Slope - rand_slope)/(median(msigs$Slope, na.rm = TRUE)-rand_slope)
    coherence = data.frame(Disease = dis$Disease, Coherence = coherence, Msig_Norm = median(msigs$Slope, na.rm = TRUE), Rand_Norm = rand_slope )      
      coherence_tab = bind_rows(coherence, coherence_tab)
      saveRDS(coherence_tab, "coherence_string_filt.rds")
}

```{r}
msig = readRDS("KEGG_Biogrid.rds")
msig =msig %>% filter(Category == "CP:KEGG")
coherence_tab = bind_rows()
for (i in unique(dis_slopes_biogrid_count$Disease)) {
  print(i)
  dis = dis_slopes_biogrid_count %>% filter(Disease == i)
  msigs = msig %>% mutate(Num_Genes = abs(Count-dis$Count)) %>% arrange(Num_Genes)
  msigs = msigs[msigs$Num_Genes %in% unique(msigs$Num_Genes)[1:10],]

  diseases = bind_rows()
  j = 1
    while(j<11) {
    diseases_curr = GeneSample(dis$Count, string, directed = FALSE)
    diseases_curr = data.frame(Gene = names(diseases_curr$internal_connectivity), Internal = sqrt(diseases_curr$internal_connectivity), External = sqrt(diseases_curr$external_connectivity))
    if (any(diseases_curr$Internal !=0)) {
      j = j+1
      diseases = bind_rows(diseases, diseases_curr)

    }
    }

      mod_rand = lm(External ~ Internal-1, data = diseases)
      rand_slope = coef(mod_rand)[[1]]

      coherence = (dis$Slope - rand_slope)/(median(msigs$Slope, na.rm = TRUE)-rand_slope)
      coherence = data.frame(Disease = dis$Disease, Coherence = coherence, Msig_Norm = median(msigs$Slope, na.rm = TRUE), Rand_Norm = rand_slope )      
      coherence_tab = bind_rows(coherence, coherence_tab)
      saveRDS(coherence_tab, "coherence_biogrid.rds")
}

# Reactome

```{r}
msig = readRDS("KEGG_String.rds")
msig =msig %>% filter(Category == "CP:REACTOME") %>% filter(!is.na(Slope))
coherence_tab = bind_rows()
for (i in unique(dis_slopes_string_count$Disease)) {
  print(i)
  dis = dis_slopes_string_count %>% filter(Disease == i)
  msigs = msig %>% mutate(Num_Genes = abs(Count-dis$Count)) %>% arrange(Num_Genes)
  msigs = msigs[msigs$Num_Genes %in% unique(msigs$Num_Genes)[1:10],]

  diseases = bind_rows()
  j = 1
    while(j<11) {
    diseases_curr = GeneSample(dis$Count, string, directed = FALSE)
    diseases_curr = data.frame(Gene = names(diseases_curr$internal_connectivity), Internal = sqrt(diseases_curr$internal_connectivity), External = sqrt(diseases_curr$external_connectivity))
    if (any(diseases_curr$Internal !=0)) {
      j = j+1
      diseases = bind_rows(diseases, diseases_curr)

    }
    }

      mod_rand = lm(External ~ Internal-1, data = diseases)
      rand_slope = coef(mod_rand)[[1]]

      coherence = (dis$Slope - rand_slope)/(median(msigs$Slope, na.rm = TRUE)-rand_slope)
      coherence = data.frame(Disease = dis$Disease, Coherence = coherence, Msig_Norm = median(msigs$Slope, na.rm = TRUE), Rand_Norm = rand_slope )

      coherence_tab = bind_rows(coherence, coherence_tab)
      saveRDS(coherence_tab, "coherence_string_react.rds")
}

```{r}
msig = readRDS("KEGG_String_Filt.rds")
msig =msig %>% filter(Category == "CP:REACTOME") %>% filter(!is.na(Slope))
coherence_tab = bind_rows()
for (i in unique(dis_slopes_string_filt_count$Disease)) {
  print(i)
  dis = dis_slopes_string_filt_count %>% filter(Disease == i)
  msigs = msig %>% mutate(Num_Genes = abs(Count-dis$Count)) %>% arrange(Num_Genes)
  msigs = msigs[msigs$Num_Genes %in% unique(msigs$Num_Genes)[1:10],]

  diseases = bind_rows()
  j = 1
    while(j<11) {
    diseases_curr = GeneSample(dis$Count, string, directed = FALSE)
    diseases_curr = data.frame(Gene = names(diseases_curr$internal_connectivity), Internal = sqrt(diseases_curr$internal_connectivity), External = sqrt(diseases_curr$external_connectivity))
    if (any(diseases_curr$Internal !=0)) {
      j = j+1
      diseases = bind_rows(diseases, diseases_curr)

    }
    }

      mod_rand = lm(External ~ Internal-1, data = diseases)
      rand_slope = coef(mod_rand)[[1]]

      coherence = (dis$Slope - rand_slope)/(median(msigs$Slope, na.rm = TRUE)-rand_slope)
      coherence = data.frame(Disease = dis$Disease, Coherence = coherence)

      coherence_tab = bind_rows(coherence, coherence_tab)
      saveRDS(coherence_tab, "coherence_string_filt_react.rds")
}

```{r}
msig = readRDS("KEGG_Biogrid.rds")
msig =msig %>% filter(Category == "CP:REACTOME") %>% filter(!is.na(Slope))
coherence_tab = bind_rows()
for (i in unique(dis_slopes_biogrid_count$Disease)) {
  print(i)
  dis = dis_slopes_biogrid_count %>% filter(Disease == i)
  msigs = msig %>% mutate(Num_Genes = abs(Count-dis$Count)) %>% arrange(Num_Genes)
  msigs = msigs[msigs$Num_Genes %in% unique(msigs$Num_Genes)[1:10],]

  diseases = bind_rows()
  j = 1
    while(j<11) {
    diseases_curr = GeneSample(dis$Count, string, directed = FALSE)
    diseases_curr = data.frame(Gene = names(diseases_curr$internal_connectivity), Internal = sqrt(diseases_curr$internal_connectivity), External = sqrt(diseases_curr$external_connectivity))
    if (any(diseases_curr$Internal !=0)) {
      j = j+1
      diseases = bind_rows(diseases, diseases_curr)

    }
    }

      mod_rand = lm(External ~ Internal-1, data = diseases)
      rand_slope = coef(mod_rand)[[1]]

      coherence = (dis$Slope - rand_slope)/(median(msigs$Slope, na.rm = TRUE)-rand_slope)
      coherence = data.frame(Disease = dis$Disease, Coherence = coherence)

      coherence_tab = bind_rows(coherence, coherence_tab)
      saveRDS(coherence_tab, "coherence_biogrid_react.rds")
}

# CC

```{r}
msig = readRDS("KEGG_String.rds")
msig =msig %>% filter(Category == "CC") %>% filter(!is.na(Slope))
coherence_tab = bind_rows()
for (i in unique(dis_slopes_string_count$Disease)) {
  print(i)
  dis = dis_slopes_string_count %>% filter(Disease == i)
  msigs = msig %>% mutate(Num_Genes = abs(Count-dis$Count)) %>% arrange(Num_Genes)
  msigs = msigs[msigs$Num_Genes %in% unique(msigs$Num_Genes)[1:10],]

  diseases = bind_rows()
  j = 1
    while(j<11) {
    diseases_curr = GeneSample(dis$Count, string, directed = FALSE)
    diseases_curr = data.frame(Gene = names(diseases_curr$internal_connectivity), Internal = sqrt(diseases_curr$internal_connectivity), External = sqrt(diseases_curr$external_connectivity))
    if (any(diseases_curr$Internal !=0)) {
      j = j+1
      diseases = bind_rows(diseases, diseases_curr)

    }
    }

      mod_rand = lm(External ~ Internal-1, data = diseases)
      rand_slope = coef(mod_rand)[[1]]

      coherence = (dis$Slope - rand_slope)/(median(msigs$Slope, na.rm = TRUE)-rand_slope)
      coherence = data.frame(Disease = dis$Disease, Coherence = coherence, Msig_Norm = median(msigs$Slope, na.rm = TRUE), Rand_Norm = rand_slope )

      coherence_tab = bind_rows(coherence, coherence_tab)
      saveRDS(coherence_tab, "coherence_string_CC.rds")
}

```{r}
msig = readRDS("KEGG_String_Filt.rds")
msig =msig %>% filter(Category == "CC") %>% filter(!is.na(Slope))
coherence_tab = bind_rows()
for (i in unique(dis_slopes_string_filt_count$Disease)) {
  print(i)
  dis = dis_slopes_string_filt_count %>% filter(Disease == i)
  msigs = msig %>% mutate(Num_Genes = abs(Count-dis$Count)) %>% arrange(Num_Genes)
  msigs = msigs[msigs$Num_Genes %in% unique(msigs$Num_Genes)[1:10],]

  diseases = bind_rows()
  j = 1
    while(j<11) {
    diseases_curr = GeneSample(dis$Count, string, directed = FALSE)
    diseases_curr = data.frame(Gene = names(diseases_curr$internal_connectivity), Internal = sqrt(diseases_curr$internal_connectivity), External = sqrt(diseases_curr$external_connectivity))
    if (any(diseases_curr$Internal !=0)) {
      j = j+1
      diseases = bind_rows(diseases, diseases_curr)

    }
    }

      mod_rand = lm(External ~ Internal-1, data = diseases)
      rand_slope = coef(mod_rand)[[1]]

      coherence = (dis$Slope - rand_slope)/(median(msigs$Slope, na.rm = TRUE)-rand_slope)
      coherence = data.frame(Disease = dis$Disease, Coherence = coherence)

      coherence_tab = bind_rows(coherence, coherence_tab)
      saveRDS(coherence_tab, "coherence_string_filt_CC.rds")
}

```{r}
msig = readRDS("KEGG_Biogrid.rds")
msig =msig %>% filter(Category == "CC") %>% filter(!is.na(Slope))
coherence_tab = bind_rows()
for (i in unique(dis_slopes_biogrid_count$Disease)) {
  print(i)
  dis = dis_slopes_biogrid_count %>% filter(Disease == i)
  msigs = msig %>% mutate(Num_Genes = abs(Count-dis$Count)) %>% arrange(Num_Genes)
  msigs = msigs[msigs$Num_Genes %in% unique(msigs$Num_Genes)[1:10],]

  diseases = bind_rows()
  j = 1
    while(j<11) {
    diseases_curr = GeneSample(dis$Count, string, directed = FALSE)
    diseases_curr = data.frame(Gene = names(diseases_curr$internal_connectivity), Internal = sqrt(diseases_curr$internal_connectivity), External = sqrt(diseases_curr$external_connectivity))
    if (any(diseases_curr$Internal !=0)) {
      j = j+1
      diseases = bind_rows(diseases, diseases_curr)

    }
    }

      mod_rand = lm(External ~ Internal-1, data = diseases)
      rand_slope = coef(mod_rand)[[1]]

      coherence = (dis$Slope - rand_slope)/(median(msigs$Slope, na.rm = TRUE)-rand_slope)
      coherence = data.frame(Disease = dis$Disease, Coherence = coherence)

      coherence_tab = bind_rows(coherence, coherence_tab)
      saveRDS(coherence_tab, "coherence_biogrid_CC.rds")
}

>>>>

# ```{r}
# #Repeating for string
# 
# data_dir = "./data/"
# 
# #Read in new string database
# 
# string = read_table2(paste0(data_dir,"9606.protein.links.v11.0.txt.gz"))
# 
# string = string %>% mutate(protein1 = gsub("9606.", "", protein1), 
#                              protein2 = gsub("9606.", "", protein2))
# 
# #Read in ensemble protein ID
# 
# ensembl = biomaRt::useEnsembl(biomart="ensembl", dataset="hsapiens_gene_ensembl", mirror = "www")
# 
# #Get gene set
# genes = biomaRt::getBM(attributes=c('ensembl_peptide_id','hgnc_symbol'), mart = ensembl)
# 
# 
# #Join gene names with string
# 
# string = left_join(string, genes, by = c("protein1" = "ensembl_peptide_id", "protein2" = "ensembl_peptide_id"))
# 
# #Rename to work with our functions
# 
# string = string %>% dplyr::rename(hgnc_symbol_a = hgnc_symbol)
# 
# #Repeat for second set of proteins
# 
# string = left_join(string, genes, by = c("protein2" = "ensembl_peptide_id"))
# 
# string = string %>% dplyr::rename(hgnc_symbol_b = hgnc_symbol)
# 
# string_filt = string %>% filter(combined_score>=500)
# 
# dim(string)
# ```
# 
# ```{r}
# #Reading in biogrid data
# 
# links = read_tsv("./data/BIOGRID-ALL-3.5.174.mitab.txt")
# 
# #Select human protein-protein interactions
# 
# links = links %>% filter(`Taxid Interactor A` == "taxid:9606" & `Taxid Interactor B` == "taxid:9606")
# 
# #Split based on Biogrid ID system then pull out gene names
# 
# protein1 = lapply(strsplit(links$`Alt IDs Interactor A`, "locuslink:"), function(x) strsplit(x[2], "\\|")[[1]][1])
# protein2 = lapply(strsplit(links$`Alt IDs Interactor B`, "locuslink:"), function(x) strsplit(x[2], "\\|")[[1]][1])
# 
# protein1 = unlist(protein1)
# protein2 = unlist(protein2)
# 
# #Place into matrix in form that disease2frame works on
# 
# links = links %>% mutate(protein1 =protein1, 
#                              protein2 = protein2) %>% dplyr::select(protein1, protein2)
# 
# links = links %>% dplyr::select(hgnc_symbol_a = protein1,hgnc_symbol_b = protein2)
# 
# 
# dim(links)
# ```
# 
# ```{r}
# #Read in edges generated from Connectivity_Comparison_*.Rmd
# 
# disease_overall_string = readRDS("string_edges_new.rds")
# 
# disease_overall_string_filt = readRDS("string_filt_edges_new.rds")
# 
# disease_overall_biogrid = readRDS("biogrid_edges_new.rds")
# 
# #Calculate slopes for all diseases under each category
# 
# dis_slopes_string_count = disease_overall_string %>% filter(Internal != 0) %>% filter(Category != "Random") %>% filter(Category != "KEGG") %>% 
#     group_by(Disease, Category) %>% mutate(Count = n()) %>% group_by(Disease, Category, Count) %>%
#     do({
#       mod = lm(sqrt(External) ~ sqrt(Internal)-1, data = .)
#       data.frame(Slope= coef(mod)[1])
#     }) %>% arrange(Slope) %>% filter(Count>4)
# 
# dis_slopes_string_filt_count = disease_overall_string_filt %>% filter(Internal != 0) %>% filter(Category != "Random") %>% filter(Category != "KEGG") %>% 
#     group_by(Disease, Category) %>% mutate(Count = n()) %>% group_by(Disease, Category, Count) %>%
#     do({
#       mod = lm(sqrt(External) ~ sqrt(Internal)-1, data = .)
#       data.frame(Slope= coef(mod)[1])
#     }) %>% arrange(Slope) %>% filter(Count>4)
# 
# dis_slopes_biogrid_count = disease_overall_biogrid %>% filter(Internal != 0) %>% filter(Category != "Random") %>% filter(Category != "KEGG") %>% 
#     group_by(Disease, Category) %>% mutate(Count = n()) %>% group_by(Disease, Category, Count) %>%
#     do({
#       mod = lm(sqrt(External) ~ sqrt(Internal)-1, data = .)
#       data.frame(Slope= coef(mod)[1])
#     }) %>% arrange(Slope) %>% filter(Count>4)
# 
# 
# #Running coherence for string
# 
# #Read in KEGG pathways for coherence
# msig = readRDS("KEGG_String.rds")
# msig =msig %>% filter(Category == "CP:KEGG")
# coherence_tab = bind_rows()
# for (i in unique(dis_slopes_string_count$Disease)) {
#   #Filter to only include specific disease coherence
#   dis = dis_slopes_string_count %>% ungroup() %>% filter(Disease == i)
#   #Get closest KEGG pathways in term of gene counts
#   msigs = msig %>% mutate(Num_Genes = abs(Count-dis$Count)) %>% arrange(Num_Genes)
#   #Take top 10 KEGG pathways
#   msigs = msigs[msigs$Num_Genes %in% unique(msigs$Num_Genes)[1:10],]
#   
#   diseases = bind_rows()
#   #Generate random networks
#   j = 1
#     while(j<11) {
#     #Sample gene networks equal in size to disease count
#     diseases_curr = GeneSample(dis$Count, string, directed = FALSE)
#     #Get random gene networks
#     diseases_curr = data.frame(Gene = names(diseases_curr$internal_connectivity), Internal = sqrt(diseases_curr$internal_connectivity), External = sqrt(diseases_curr$external_connectivity))
#     
#     #Repeat if there are no internal edges
#     if (any(diseases_curr$Internal !=0)) {
#       j = j+1
#       diseases = bind_rows(diseases, diseases_curr)
# 
#     }
#     }
#     #Calculate overall slope of random disease networks
#       mod_rand = lm(External ~ Internal-1, data = diseases)
#       rand_slope = coef(mod_rand)[[1]]
#       
#       #Normalize based on random slope and the median of kegg slopes (More robust)
#       coherence = (dis$Slope - rand_slope)/(median(msigs$Slope, na.rm = TRUE)-rand_slope)
#       coherence = data.frame(Disease = dis$Disease, Coherence = coherence, Msig_Norm = median(msigs$Slope, na.rm = TRUE), Rand_Norm = rand_slope )      
#       coherence_tab = bind_rows(coherence, coherence_tab)
#       saveRDS(coherence_tab, "coherence_string.rds")
# }
#   
# 
# 
# ```
# 
# ```{r}
# msig = readRDS("KEGG_String_Filt.rds")
# msig =msig %>% filter(Category == "CP:KEGG")
# coherence_tab = bind_rows()
# for (i in unique(dis_slopes_string_filt_count$Disease)) {
#   print(i)
#   dis = dis_slopes_string_filt_count %>% filter(Disease == i)
#   msigs = msig %>% mutate(Num_Genes = abs(Count-dis$Count)) %>% arrange(Num_Genes)
#   msigs = msigs[msigs$Num_Genes %in% unique(msigs$Num_Genes)[1:10],]
#   
#   diseases = bind_rows()
#   j = 1
#     while(j<11) {
#     diseases_curr = GeneSample(dis$Count, string, directed = FALSE)
#     diseases_curr = data.frame(Gene = names(diseases_curr$internal_connectivity), Internal = sqrt(diseases_curr$internal_connectivity), External = sqrt(diseases_curr$external_connectivity))
#     if (any(diseases_curr$Internal !=0)) {
#       j = j+1
#       diseases = bind_rows(diseases, diseases_curr)
# 
#     }
#     }
#   
#       mod_rand = lm(External ~ Internal-1, data = diseases)
#       rand_slope = coef(mod_rand)[[1]]
#       
#       coherence = (dis$Slope - rand_slope)/(median(msigs$Slope, na.rm = TRUE)-rand_slope)
#     coherence = data.frame(Disease = dis$Disease, Coherence = coherence, Msig_Norm = median(msigs$Slope, na.rm = TRUE), Rand_Norm = rand_slope )      
#       coherence_tab = bind_rows(coherence, coherence_tab)
#       saveRDS(coherence_tab, "coherence_string_filt.rds")
# }
#   
#   
# ```
# 
# ```{r}
# msig = readRDS("KEGG_Biogrid.rds")
# msig =msig %>% filter(Category == "CP:KEGG")
# coherence_tab = bind_rows()
# for (i in unique(dis_slopes_biogrid_count$Disease)) {
#   print(i)
#   dis = dis_slopes_biogrid_count %>% filter(Disease == i)
#   msigs = msig %>% mutate(Num_Genes = abs(Count-dis$Count)) %>% arrange(Num_Genes)
#   msigs = msigs[msigs$Num_Genes %in% unique(msigs$Num_Genes)[1:10],]
#   
#   diseases = bind_rows()
#   j = 1
#     while(j<11) {
#     diseases_curr = GeneSample(dis$Count, string, directed = FALSE)
#     diseases_curr = data.frame(Gene = names(diseases_curr$internal_connectivity), Internal = sqrt(diseases_curr$internal_connectivity), External = sqrt(diseases_curr$external_connectivity))
#     if (any(diseases_curr$Internal !=0)) {
#       j = j+1
#       diseases = bind_rows(diseases, diseases_curr)
# 
#     }
#     }
#   
#       mod_rand = lm(External ~ Internal-1, data = diseases)
#       rand_slope = coef(mod_rand)[[1]]
#       
#       coherence = (dis$Slope - rand_slope)/(median(msigs$Slope, na.rm = TRUE)-rand_slope)
#       coherence = data.frame(Disease = dis$Disease, Coherence = coherence, Msig_Norm = median(msigs$Slope, na.rm = TRUE), Rand_Norm = rand_slope )      
#       coherence_tab = bind_rows(coherence, coherence_tab)
#       saveRDS(coherence_tab, "coherence_biogrid.rds")
# }
#   
#   
# ```
# 
# # Reactome
# 
# ```{r}
# msig = readRDS("KEGG_String.rds")
# msig =msig %>% filter(Category == "CP:REACTOME") %>% filter(!is.na(Slope))
# coherence_tab = bind_rows()
# for (i in unique(dis_slopes_string_count$Disease)) {
#   print(i)
#   dis = dis_slopes_string_count %>% filter(Disease == i)
#   msigs = msig %>% mutate(Num_Genes = abs(Count-dis$Count)) %>% arrange(Num_Genes)
#   msigs = msigs[msigs$Num_Genes %in% unique(msigs$Num_Genes)[1:10],]
#   
#   diseases = bind_rows()
#   j = 1
#     while(j<11) {
#     diseases_curr = GeneSample(dis$Count, string, directed = FALSE)
#     diseases_curr = data.frame(Gene = names(diseases_curr$internal_connectivity), Internal = sqrt(diseases_curr$internal_connectivity), External = sqrt(diseases_curr$external_connectivity))
#     if (any(diseases_curr$Internal !=0)) {
#       j = j+1
#       diseases = bind_rows(diseases, diseases_curr)
# 
#     }
#     }
#   
#       mod_rand = lm(External ~ Internal-1, data = diseases)
#       rand_slope = coef(mod_rand)[[1]]
#       
#       coherence = (dis$Slope - rand_slope)/(median(msigs$Slope, na.rm = TRUE)-rand_slope)
#       coherence = data.frame(Disease = dis$Disease, Coherence = coherence, Msig_Norm = median(msigs$Slope, na.rm = TRUE), Rand_Norm = rand_slope )
#       
#       coherence_tab = bind_rows(coherence, coherence_tab)
#       saveRDS(coherence_tab, "coherence_string_react.rds")
# }
#   
# 
# ```
# 
# ```{r}
# msig = readRDS("KEGG_String_Filt.rds")
# msig =msig %>% filter(Category == "CP:REACTOME") %>% filter(!is.na(Slope))
# coherence_tab = bind_rows()
# for (i in unique(dis_slopes_string_filt_count$Disease)) {
#   print(i)
#   dis = dis_slopes_string_filt_count %>% filter(Disease == i)
#   msigs = msig %>% mutate(Num_Genes = abs(Count-dis$Count)) %>% arrange(Num_Genes)
#   msigs = msigs[msigs$Num_Genes %in% unique(msigs$Num_Genes)[1:10],]
#   
#   diseases = bind_rows()
#   j = 1
#     while(j<11) {
#     diseases_curr = GeneSample(dis$Count, string, directed = FALSE)
#     diseases_curr = data.frame(Gene = names(diseases_curr$internal_connectivity), Internal = sqrt(diseases_curr$internal_connectivity), External = sqrt(diseases_curr$external_connectivity))
#     if (any(diseases_curr$Internal !=0)) {
#       j = j+1
#       diseases = bind_rows(diseases, diseases_curr)
# 
#     }
#     }
#   
#       mod_rand = lm(External ~ Internal-1, data = diseases)
#       rand_slope = coef(mod_rand)[[1]]
#       
#       coherence = (dis$Slope - rand_slope)/(median(msigs$Slope, na.rm = TRUE)-rand_slope)
#       coherence = data.frame(Disease = dis$Disease, Coherence = coherence)
#       
#       coherence_tab = bind_rows(coherence, coherence_tab)
#       saveRDS(coherence_tab, "coherence_string_filt_react.rds")
# }
#   
#   
# ```
# 
# ```{r}
# msig = readRDS("KEGG_Biogrid.rds")
# msig =msig %>% filter(Category == "CP:REACTOME") %>% filter(!is.na(Slope))
# coherence_tab = bind_rows()
# for (i in unique(dis_slopes_biogrid_count$Disease)) {
#   print(i)
#   dis = dis_slopes_biogrid_count %>% filter(Disease == i)
#   msigs = msig %>% mutate(Num_Genes = abs(Count-dis$Count)) %>% arrange(Num_Genes)
#   msigs = msigs[msigs$Num_Genes %in% unique(msigs$Num_Genes)[1:10],]
#   
#   diseases = bind_rows()
#   j = 1
#     while(j<11) {
#     diseases_curr = GeneSample(dis$Count, string, directed = FALSE)
#     diseases_curr = data.frame(Gene = names(diseases_curr$internal_connectivity), Internal = sqrt(diseases_curr$internal_connectivity), External = sqrt(diseases_curr$external_connectivity))
#     if (any(diseases_curr$Internal !=0)) {
#       j = j+1
#       diseases = bind_rows(diseases, diseases_curr)
# 
#     }
#     }
#   
#       mod_rand = lm(External ~ Internal-1, data = diseases)
#       rand_slope = coef(mod_rand)[[1]]
#       
#       coherence = (dis$Slope - rand_slope)/(median(msigs$Slope, na.rm = TRUE)-rand_slope)
#       coherence = data.frame(Disease = dis$Disease, Coherence = coherence)
#       
#       coherence_tab = bind_rows(coherence, coherence_tab)
#       saveRDS(coherence_tab, "coherence_biogrid_react.rds")
# }
#   
#   
# ```
# 
# # CC
# 
# ```{r}
# msig = readRDS("KEGG_String.rds")
# msig =msig %>% filter(Category == "CC") %>% filter(!is.na(Slope))
# coherence_tab = bind_rows()
# for (i in unique(dis_slopes_string_count$Disease)) {
#   print(i)
#   dis = dis_slopes_string_count %>% filter(Disease == i)
#   msigs = msig %>% mutate(Num_Genes = abs(Count-dis$Count)) %>% arrange(Num_Genes)
#   msigs = msigs[msigs$Num_Genes %in% unique(msigs$Num_Genes)[1:10],]
#   
#   diseases = bind_rows()
#   j = 1
#     while(j<11) {
#     diseases_curr = GeneSample(dis$Count, string, directed = FALSE)
#     diseases_curr = data.frame(Gene = names(diseases_curr$internal_connectivity), Internal = sqrt(diseases_curr$internal_connectivity), External = sqrt(diseases_curr$external_connectivity))
#     if (any(diseases_curr$Internal !=0)) {
#       j = j+1
#       diseases = bind_rows(diseases, diseases_curr)
# 
#     }
#     }
#   
#       mod_rand = lm(External ~ Internal-1, data = diseases)
#       rand_slope = coef(mod_rand)[[1]]
#       
#       coherence = (dis$Slope - rand_slope)/(median(msigs$Slope, na.rm = TRUE)-rand_slope)
#       coherence = data.frame(Disease = dis$Disease, Coherence = coherence, Msig_Norm = median(msigs$Slope, na.rm = TRUE), Rand_Norm = rand_slope )
#       
#       coherence_tab = bind_rows(coherence, coherence_tab)
#       saveRDS(coherence_tab, "coherence_string_CC.rds")
# }
#   
# 
# ```
# 
# ```{r}
# msig = readRDS("KEGG_String_Filt.rds")
# msig =msig %>% filter(Category == "CC") %>% filter(!is.na(Slope))
# coherence_tab = bind_rows()
# for (i in unique(dis_slopes_string_filt_count$Disease)) {
#   print(i)
#   dis = dis_slopes_string_filt_count %>% filter(Disease == i)
#   msigs = msig %>% mutate(Num_Genes = abs(Count-dis$Count)) %>% arrange(Num_Genes)
#   msigs = msigs[msigs$Num_Genes %in% unique(msigs$Num_Genes)[1:10],]
#   
#   diseases = bind_rows()
#   j = 1
#     while(j<11) {
#     diseases_curr = GeneSample(dis$Count, string, directed = FALSE)
#     diseases_curr = data.frame(Gene = names(diseases_curr$internal_connectivity), Internal = sqrt(diseases_curr$internal_connectivity), External = sqrt(diseases_curr$external_connectivity))
#     if (any(diseases_curr$Internal !=0)) {
#       j = j+1
#       diseases = bind_rows(diseases, diseases_curr)
# 
#     }
#     }
#   
#       mod_rand = lm(External ~ Internal-1, data = diseases)
#       rand_slope = coef(mod_rand)[[1]]
#       
#       coherence = (dis$Slope - rand_slope)/(median(msigs$Slope, na.rm = TRUE)-rand_slope)
#       coherence = data.frame(Disease = dis$Disease, Coherence = coherence)
#       
#       coherence_tab = bind_rows(coherence, coherence_tab)
#       saveRDS(coherence_tab, "coherence_string_filt_CC.rds")
# }
#   
#   
# ```
# 
# ```{r}
# msig = readRDS("KEGG_Biogrid.rds")
# msig =msig %>% filter(Category == "CC") %>% filter(!is.na(Slope))
